---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TestNewPackage

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/EV201/TestNewPackage.svg?branch=master)](https://travis-ci.com/EV201/TestNewPackage)
<!-- badges: end -->

The goal of TestNewPackage is to test R with Github for the an assignment in the 'building R packages' Coursera course.

## Installation

You can install the released version of TestNewPackage from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("TestNewPackage")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EV201/TestNewPackage")
```

## Accident statistics
The fars functions use the buildin databases: accident_2013.csv.bz2, accident_2014.csv.bz2, accident_2015.csv.bz2
You can access these databases directly by system.file("extdata", filename, package = "TestNewPackage")

The fars functions show a summary of the accidents per month and year (fars_summarize_years()) or the accidents for a year on a map for a state (fars_map_state()). Only the years 2013-2015 can be used.

## Examples
```{r setup}
library(TestNewPackage)
```

summarizing accidents for a year:
```{r summarize, echo = TRUE}
fars_summarize_years(2013)
```

or plotting the accidents for a year on a state map:
```{r mapping, echo = TRUE}
fars_map_state(1, 2015)
```
