---
title: "fars"
output: rmarkdown::html_vignette
date: "2020-09-23"
vignette: >
  %\VignetteIndexEntry{fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TestNewPackage)
```

This is an example package for the accidents in the different states and years in the USA.

The fars functions use the buildin databases: accident_2013.csv.bz2, accident_2014.csv.bz2, accident_2015.csv.bz2
You can access these databases directly by system.file("extdata", filename, package = "TestNewPackage")

The fars functions show a summary of the accidents per month and year (fars_summarize_years()) or the accidents for a year on a map for a state (fars_map_state()). Only the years 2013-2015 can be used.

Example usage:
summarizing accidents for a year:
``` r
fars_summarize_years(2013)
```

or plotting the accidents for a year on a state map:
``` r
fars_map_state(1, 2015)
```
